Simulation Study: Varying Effect Size

### 2018-09-06 datasets/simulations/simulations-uasettings-t.Rmd
Move simulation Rmds around, suppl into separate dir

---
title: "Simulation Study: Varying Effect Size (t-11)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "varyinges-t-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "varyinges-t-benchmark-flattop.rds")
skew_file <- file.path(resdir, "varyinges-t-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "varyinges-t-benchmark-bimodal.rds")

@@

As described in `simulations-null.Rmd`, we include Scott's FDR Regression in the analysis
for simulations with Gaussian or t-distributed test statistics. Again, we include both
`nulltype = "empirical"` and `nulltype = "theoretical"`. Since all settings in this
series of simulations use test statistics simulated with t-distributed test statistics,
we include Scott's FDR Regression in all of the comparisons.

@@

Since all simulation settings in this case study use t-distributed test statistics, we must specify
the number of degrees of freedom for ASH. We add an additional parameter to the `ashq`
method with the corresponding degrees of freedom of the test statistic distribution.

@@

```{r spiky-parameters}
es_dist <- sampler_spiky       # functional: dist of alternative test stats
seed <- 778
```

@@

```{r flattop-parameters}
es_dist <- sampler_flat_top       # functional: dist of alternative test stats
seed <- 980
```

@@

```{r skew-parameters}
es_dist <- sampler_skew       # functional: dist of alternative test stats
seed <- 206
```

@@

```{r bimodal-parameters}
es_dist <- sampler_bimodal       # functional: dist of alternative test stats
seed <- 913
```

>>>>

---
title: "Simulation Study: Unimodal Settings (t test statistics)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "uasettings-t-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "uasettings-t-benchmark-flattop.rds")
skew_file <- file.path(resdir, "uasettings-t-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "uasettings-t-benchmark-bimodal.rds")

@@

As described in `simulations-null.Rmd`, we include Scott's FDR Regression in the analysis
for simulations with Gaussian or t-distributed test statistics. Again, we include both
`nulltype = "empirical"` and `nulltype = "theoretical"`. Since all settings in this
series of simulations use t-distributed test statistics, we include Scott's FDR Regression
in all of the comparisons.

@@

Since all simulation settings in this case study use t-distributed test statistics, we must specify
the number of degrees of freedom for ASH. We add an additional parameter to the `ashq`
method with the corresponding degrees of freedom of the test statistics.

@@

```{r spiky-parameters}
es_dist <- function(n) { 2*sampler_spiky(n) }       # functional: dist of alternative test stats
seed <- 778
```

@@

```{r flattop-parameters}
es_dist <- function(n) { 2*sampler_flat_top(n) }       # functional: dist of alternative test stats
seed <- 980
```

@@

```{r skew-parameters}
es_dist <- function(n) { 2*sampler_skew(n) }       # functional: dist of alternative test stats
seed <- 206
```

@@

```{r bimodal-parameters}
es_dist <- function(n) { 2*sampler_bimodal(n) }       # functional: dist of alternative test stats
seed <- 913
```

### 2018-09-06 datasets/simulations/simulations-uasettings.Rmd
Move simulation Rmds around, suppl into separate dir

---
title: "Simulation Study: Unimodal Settings (t test statistics)"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. An informative covariate is included in the setting as described in
`simulations-informative-cubic.Rmd`. This set of simulations is similar to those
presented in `simulations-varyingeffectsize.Rmd`, however, t-distributed test
statistics are used.

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "uasettings-t-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "uasettings-t-benchmark-flattop.rds")
skew_file <- file.path(resdir, "uasettings-t-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "uasettings-t-benchmark-bimodal.rds")

@@

As described in `simulations-null.Rmd`, we include Scott's FDR Regression in the analysis
for simulations with Gaussian or t-distributed test statistics. Again, we include both
`nulltype = "empirical"` and `nulltype = "theoretical"`. Since all settings in this
series of simulations use t-distributed test statistics, we include Scott's FDR Regression
in all of the comparisons.

@@

Since all simulation settings in this case study use t-distributed test statistics, we must specify
the number of degrees of freedom for ASH. We add an additional parameter to the `ashq`
method with the corresponding degrees of freedom of the test statistics.

```{r}
bdplus <- modifyBMethod(bdplus, "ashq", df = 11)
```

@@

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_cubic(0.90)              # numeric: proportion of null hypotheses
ts_dist <- rt_perturber(11)         # functional: sampling dist/noise for test stats
null_dist <- rt_2pvaluer(11)        # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```

>>>>

---
title: "Simulation Study: Unimodal Settings"
author: "Patrick Kimes"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: 
   html_document:
        toc: true
        toc_float: true
        highlight: tango
        number_sections: true
---

@@

In this set of simulations, we consider settings with both null and non-null
tests with varying distribution of effect sizes under the non-null (alternative)
setting. An informative covariate is included in the setting as described in
`simulations-informative-cubic.Rmd`.

@@

## intermediary files we create below
spiky_file <- file.path(resdir, "uasettings-benchmark-spiky.rds")
flattop_file <- file.path(resdir, "varyinges-benchmark-flattop.rds")
skew_file <- file.path(resdir, "uasettings-benchmark-skew.rds")
bimodal_file <- file.path(resdir, "uasettings-benchmark-bimodal.rds")

@@

As described in `simulations-null.Rmd`, we include Scott's FDR Regression in the analysis
for simulations with Gaussian or t-distributed test statistics. Again, we include both
`nulltype = "empirical"` and `nulltype = "theoretical"`. Since all settings in this
series of simulations use Gaussian test statistics, we include Scott's FDR Regression
in all of the comparisons.

@@

@@

```{r parameters-shared}
m <- 20000                          # integer: number of hypothesis tests
pi0 <- pi0_cubic(0.90)              # numeric: proportion of null hypotheses
ts_dist <- rnorm_perturber(1)       # functional: sampling dist/noise for test stats
null_dist <- rnorm_2pvaluer(1)      # functional: dist to calc p-values
icovariate <- runif                 # functional: independent covariate
```

### 2018-09-06 datasets/simulations/simulations-varyinginformativeness-discrete.Rmd
Move simulation Rmds around, suppl into separate dir

## intermediary files we create below
info00_file <- file.path(resdir, "varyinginfo-benchmark-level00.rds")
info20_file <- file.path(resdir, "varyinginfo-benchmark-level20.rds")
info40_file <- file.path(resdir, "varyinginfo-benchmark-level40.rds")
info60_file <- file.path(resdir, "varyinginfo-benchmark-level60.rds")
info80_file <- file.path(resdir, "varyinginfo-benchmark-level80.rds")
info100_file <- file.path(resdir, "varyinginfo-benchmark-level100.rds")

>>>>

## intermediary files we create below
info00_file <- file.path(resdir, "varyinginfo-discrete-benchmark-level00.rds")
info20_file <- file.path(resdir, "varyinginfo-discrete-benchmark-level20.rds")
info40_file <- file.path(resdir, "varyinginfo-discrete-benchmark-level40.rds")
info60_file <- file.path(resdir, "varyinginfo-discrete-benchmark-level60.rds")
info80_file <- file.path(resdir, "varyinginfo-discrete-benchmark-level80.rds")
info100_file <- file.path(resdir, "varyinginfo-discrete-benchmark-level100.rds")

### 2018-09-06 datasets/simulations/supplementary/simulations-uasettings-originalscale.Rmd
Move simulation Rmds around, suppl into separate dir

As described in `simulations-null.Rmd`, we include Scott's FDR Regression in the analysis
for simulations with Gaussian or t-distributed noise. Again, we include both
`nulltype = "empirical"` and `nulltype = "theoretical"`. Since all settings in this
series of simulations use test statistics simulated with Gaussian noise, we include
Scott's FDR Regression in all of the comparisons.

>>>>

As described in `simulations-null.Rmd`, we include Scott's FDR Regression in the analysis
for simulations with Gaussian or t-distributed test statistics. Again, we include both
`nulltype = "empirical"` and `nulltype = "theoretical"`. Since all settings in this
series of simulations use test statistics simulated with Gaussian test statistics, we include
Scott's FDR Regression in all of the comparisons.
